\simname 2.0 User's Guide

### 2008-10-15 doc/manual.tex
git-svn-id: https://nocs.stanford.edu/cgi-bin/svn.cgi/booksim2.0/trunk@744 ce7aba0d-9f81-40a6-a495-cecae84b0515
update allocators
git-svn-id: https://nocs.stanford.edu/cgi-bin/svn.cgi/booksim2.0/trunk@763 ce7aba0d-9f81-40a6-a495-cecae84b0515

\begin{opt_list}{single}
\item[k] Network radix, the number of routers per dimension
\item[n] Network dimension
\item[c] Network concentration, the number of nodes sharing a single router. Typically set to 1, >1 only in networks that has concentration (i.e. cmesh)
\item[x] (NoC simulations only) The number of routers in the X dimension. Used to calculate channel latency between routers. 
\item[y] (NoC simulations only) The number of routers in the y dimension. Used to calculate channel latency between routers. 
\item[xr] (NoC simulations only) For networks that has c>1, the number of nodes in the x direction per router. Used to calculate channel latency between routers. 
\item[yr] (NoC simulations only) For networks that has c>1, the number of nodes in the y direction per router. Used to calculate channel latency between routers. 
\item[limit] Emulate partially filled networks. Nodes greater or equal to limit does not generate or receive packets during simulation. Though depending on the routing algorithm the routers associated with those nodes may be use to route passing by traffic.

@@

Topologies available in \simname are:
\begin{opt_list}{single}
\item[fly] A $k$-ary $n$-fly (butterfly) topology. The \texttt{k}
parameter determines the network's radix and the \texttt{n} parameter
determines the network's dimension.

@@

\item[MECS] A topology based on (***). Currently it only support 1 flit per packet.

@@

\begin{opt_list}{wait\_for\_tail\_credit}

@@

\begin{opt_list}{internal\_speedup}
\item[credit\_delay] The processing delay (in cycles) for a credit.
Does not include the wire delay for transmitting the credit.

@@

\begin{opt_list}{st\_prepare\_delay}

@@

@@

@@

@@

The NoC router (\texttt{router = noc}) is a simplified variant of the input-queued router. It does not support input or output speedup. Also, it does not support multi-cycle allocation, but does support output-first allocation.

@@

Many of the allocators used in the simulator are configurable (see
the input-queued router in Section~\ref{sec:iq_router}) and several
allocation algorithms are available.
\begin{opt_list}{wavefront}

\item[max\_size] Maximum-size matching. 
\item[islip] iSLIP separable allocator.
\item[pim] Parallel iterative matching separable allocator.
\item[loa] Lonely output allocator.
\item[wavefront] Wavefront allocator.
\item[matrix] Separable input-first allocator built from matrix arbiters.
\item[round\_robin] Separable input-first allocator built from round-robin arbiters.
\item[select] Priority-based allocator.  Allocation is performed as in
iSLIP, but with preference towards higher priority packets (see
\texttt{priority} option in Section~\ref{sec:traffic}).

@@

Allocation can also be improved by performing multiple iterations of
the algorithm and the number of iterations is controlled by the
\texttt{alloc\_iters} parameter.

@@

\begin{opt_list}{transpose}
\item[uniform] Each source sends an equal amount of traffic to each
destination (\texttt{traffic = uniform}).
\item[bitcomp] Bit complement. $d_i = \neg s_i$.
\item[bitrev] Bit reverse. $d_i = s_{b-i-1}$.
\item[shuffle] $d_i = s_{i-1 \mod b}$.
\item[transpose] $d_i = s_{i+b/2 \mod b}$.
\item[tornado] $d_x = s_x + \lceil k/2 \rceil - 1 \mod k$.
\item[neighbor] $d_x = s_x + 1 \mod k$.
\item[randperm] Random permutation.  A fixed permutation traffic
pattern is chosen uniformly at random from the set of all
permutations.  The seed used to generate this permutation is set by
the \texttt{perm\_seed} option.  So, randomly selecting values for
\texttt{perm\_seed} gives a random sampling of permutation while a
fixed value of \texttt{perm\_seed} allows the same permutation to be
used for several experiments.
\end{opt_list}

@@

\begin{opt_list}{warmup\_periods}

>>>>

\begin{opt_list}{topoparams}

\item[k] Network radix, the number of routers per dimension
\item[n] Network dimension
\item[c] Network concentration, the number of nodes sharing a single router. Typically set to 1, >1 only in networks that has concentration (i.e. cmesh)
\item[x] (NoC simulations only) The number of routers in the X dimension. Used to calculate channel latency between routers. 
\item[y] (NoC simulations only) The number of routers in the y dimension. Used to calculate channel latency between routers. 
\item[xr] (NoC simulations only) For networks that have c>1, the number of nodes in the x direction per router. Used to calculate channel latency between routers. 
\item[yr] (NoC simulations only) For networks that have c>1, the number of nodes in the y direction per router. Used to calculate channel latency between routers. 
\item[limit] Emulate partially filled networks. Nodes greater or equal to limit does not generate or receive packets during simulation. Though depending on the routing algorithm the routers associated with those nodes may be use to route passing by traffic.

@@

The channel latency of the network must be configured within the source code of the topology files. All topologies by default have channel latency of 1 cycles. Topologies available in \simname are:

\begin{opt_list}{topologies}
\item[fly] A $k$-ary $n$-fly (butterfly) topology. The \texttt{k}
parameter determines the network's radix and the \texttt{n} parameter
determines the network's dimension.

@@

\item[MECS] A topology based on ***. Currently it only support 1 flit per packet.

@@

\begin{opt_list}{flowcontrolparams}

@@

\begin{opt_list}{routerparams}
\item[credit\_delay] The processing delay (in cycles) for a credit.
Does not include the wire delay for transmitting the credit.

@@

\begin{opt_list}{iqrouterparams}

@@

\item[hold\_switch\_for\_packet]

\item[speculative] Enable speculative switch allocation (i.e., allow switch allocation to occur in parallel with VC allocation for header flits).

\item[filter\_spec\_grants] Determines how speculative grants are masked (\texttt{any\_nonspec\_gnts}: any non-speculative grant inhibits all speculative grants; \texttt{confl\_nonspec\_reqs}: speculative grants are inhibited by conflicting non-speculative requests; \texttt{confl\_nonspec\_gnts}: speculative grants are inhibited by conflicting non-speculative grants).

@@

\item[sw\_alloc\_arb\_type] The type of arbiter to use if a separable input- or output-first allocator is used for switch allocation.

@@

\item[vc\_alloc\_arb\_type] The type of arbiter to use if a separable input- or output-first allocator is used for virtual channel allocation.

@@

The NoC router (\texttt{router = noc}) is a simplified variant of the input-queued router. It does not support input or output speedup. Also, it does not support multi-cycle allocation.

@@

Many of the allocators used in the simulator are configurable (see
the input-queued router in Section~\ref{sec:iq_router}) and several
allocation algorithms are available.

\begin{opt_list}{allocators}

\item[max\_size] Maximum-size matching. 
\item[islip] iSLIP separable allocator.
\item[pim] Parallel iterative matching separable allocator.
\item[loa] Lonely output allocator.
\item[wavefront] Wavefront allocator.
\item[separable\_input\_first] Separable input-first allocator.
\item[separable\_output\_first] Separable output-first allocator.
\item[select] Priority-based allocator.  Allocation is performed as in
iSLIP, but with preference towards higher priority packets (see
\texttt{priority} option in Section~\ref{sec:traffic}).

@@

For the \texttt{islip}, \texttt{pim} and \texttt{select} allocators, allocation can be improved by performing multiple iterations of the algorithm; the number of iterations is controlled by the \texttt{alloc\_iters} parameter.

@@

\begin{opt_list}{trafficpatterns}
\item[uniform] Each source sends an equal amount of traffic to each
destination (\texttt{traffic = uniform}).
\item[bitcomp] Bit complement. $d_i = \neg s_i$.
\item[bitrev] Bit reverse. $d_i = s_{b-i-1}$.
\item[shuffle] $d_i = s_{i-1 \mod b}$.
\item[transpose] $d_i = s_{i+b/2 \mod b}$.
\item[tornado] $d_x = s_x + \lceil k/2 \rceil - 1 \mod k$.
\item[neighbor] $d_x = s_x + 1 \mod k$.
\item[randperm] Random permutation.  A fixed permutation traffic
pattern is chosen uniformly at random from the set of all
permutations.  The seed used to generate this permutation is set by
the \texttt{perm\_seed} option.  So, randomly selecting values for
\texttt{perm\_seed} gives a random sampling of permutation while a
fixed value of \texttt{perm\_seed} allows the same permutation to be
used for several experiments.
\end{opt_list}

@@

\begin{opt_list}{simparams}
